Quantifying the home advantage with `hyper3` objects

### 2023-02-08 inst/home_advantage3.Rmd
ternary plot

$$
\hat{p_1}=\frac{C}{C+D}\qquad
\hat{p_2}=\frac{B}{A+B}\qquad
M=\frac{AC-BD}{(A+B)(C+D)}
$$

@@

@@

>>>>

$$
\hat{p_1}=\frac{D}{C+D}\qquad
\hat{p_2}=\frac{B}{A+B}\qquad
\hat{M}=\frac{AC-BD}{(A+B)(C+D)}
$$

@@

Moving to the monster formulation we have

$$
\hat{p_1}=\frac{3}{7+3} = 0.3\qquad
\hat{p_2}=\frac{5}{5+9}\simeq  0.36\qquad
\hat{M}=\frac{63-21}{14\cdot 10} = 0.3
$$

@@

#  Ternary representation

```{r,label=useternary}
library(Ternary)

par(mar = rep(0.2, 4))
TernaryPlot(alab = "p1", blab = "p2", clab = "M")

FunctionToContour <- function(p1,p2,M) {
pmax(-20,log(M+p1)*A + log(p2)*B - log(M+p1+p2)*(A+B+C+D) + log(p2+M)*C + log(p1)*D )
}

# Compute and plot colour tiles
values <- TernaryPointValues(FunctionToContour, resolution = 24L)
ColourTernary(values)

# Add contour lines
TernaryContour(FunctionToContour, resolution = 36L)
```
